Hypothesis Testing

### 2019-11-08 analysis/03b_hypotheses.Rmd

---
title: "Hypotheses"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---
In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

>>>>

---
title: "Hypotheses"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

### 2019-11-08 analysis/03c_hypothesis-testing.Rmd

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    # geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}

if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       # geom_halfeyeh(.width = .95) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

# # Save plot
# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
# ggsave(
#   file_name,
#   path = here::here("analysis", "output", "figures"),
#   width = ifelse(intercept == 1, 12, 20), 
#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
#   units = "in"
# )
```

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div>

>>>>

```

#### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?

```{r}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5))
}

```

#### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?

```{r}

```

# Hypotheses:
# We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
# Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
# We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
# In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
